HSC Synthetic Pipeline I: Basic Design and Characterization of the Photometric Performance of HSC

### 2017-04-14 draft/ms_v1.tex
Song: Star-galaxy separation

    As we already mentioned, star--galaxy separation is important for cosmology survey,
    and becomes increasingly difficult for fainter and fainter objects.

        \item \plan{Explain how star--galaxy separation is done in \hscpipe{}, and
            why it is difficult at faint magnitudes.}

        \item In Fig \ref{fig:sg}, we highlight the misclassified stars and galaxies
            on the relations between the input magnitude and
            $i_{\mathrm{PSF}}-i_{\mathrm{cModel}}$.

        \item \plan{The fraction of misclassified stars show dependence on both
            input magnitude and seeing.}

        \item \plan{Most of the misclassified galaxies have $i > 24.0$.
            The fraction of misclassification and distribution of
            $i_{\mathrm{PSF}}-i_{\mathrm{cModel}}$ for synthetic galaxies also depend on
            seeings}.

@@

    \plan{Review the definition of blendedness and explain why it is important.}
    \plan{Relationship between magnitude and blendedness}

    \plan{How blendedness affects the photometric uncertainties}

>>>>

    As we already mentioned, star--galaxy separation is important for cosmology survey,
    and becomes increasingly difficult at very faint magnitude ($i<24.0$ mag). 
    In \hscpipe{}, the star--galaxy classification primarily depends on the extendedness 
    value that is measured by the magnitude difference between PSF and \cmodel{} 
    photometry in $i$-band. 
    For more details about this algorithm, please see Section 4.9.9 in Bosch\etal 
    (in prep.).

    In Fig \ref{fig:sg}, we show the current status of star--galaxy classification  
    via comparing the input magnitude with the difference between PSF and \cmodel{} 
    magnitudes for both synthetic stars and galaxies, and highlight the distributions 
    for misclassified objects. 
    As described in earlier sections, $>20$\% of synthetic stars at 
    $i_{\mathrm{Input}}>23.0$ mag is misclassified as extended objects, while only a 
    tiny fraction of faint synthetic galaxies ($i_{\mathrm{Input}}>24.0$) are 
    misclassified. 
    This confirms that the current star--galaxy classification strategy in \hscpipe{}
    results in galaxy sample with \textbf{high completeness} and star sample 
    with \textbf{high purity}.

    It it also easy to notice that seeing condition strongly modify the distributions 
    of $i_{\mathrm{PSF}}-i_{\mathrm{cModel}}$, where worse seeing clearly make it 
    more difficult to separate star and galaxy.  
    This implies that the completeness/purity of star and galaxy sample at faint end
    may depend on seeing, which deserve the attention of HSC users who care about 
    these properties.

    In the next data release, \hscpipe{} will include a better star--galaxy classifier
    that is based on Machine Learning method takes the shape and color information 
    into account. 
    We will test its improvement using \synpipe{} in the future.

@@

    In the above sections, we have pointed out the impact of high blendedness on 
    photometry through a small sample of highly blended objects.  
    Here, in Fig \ref{fig:blend}, we further explore the effect of blendedness via 
    directly plot it against the uncertainties of magnitudes and colors for both stars 
    and galaxies.
